---
title: "Assignment2"
format: pdf
editor: visual
---

```{r echo = FALSE, message = FALSE}
#installing necessary packages
rm(list=ls()) 
library(tidyverse)
library(rvest)
```

```{r}
#getting the html
url <- "https://www.motor.no/aktuelt/motors-store-vintertest-av-rekkevidde-pa-elbiler/217132"
side <- read_html(url)

#scraping website
df_car <- side %>%
html_nodes("table") %>%
.[1] %>% #using . to refer to the previous line og code
html_table()
```

```{r}
df_car <- df_car[[1]] #getting the avaliable list

colnames(df_car) <- unlist(df_car[1,]) #setting the first row to their index
df_car <- df_car[-1,]


df_car<- df_car %>% slice(-c(19, 26)) #removing rows that lacks data

#removing everything in the rows, but the first three digits to make it easier to plot
df_car$`WLTP-tall` <- substr(df_car$`WLTP-tall`, 1, 3) 
df_car$STOPP <- substr(df_car$STOPP, 1, 3)

#making the columns numeric
df_car$`WLTP-tall` <- as.numeric(df_car$`WLTP-tall`)
df_car$STOPP <- as.numeric(df_car$STOPP)
```

```{r}
#plotting 
  df_car %>%
    ggplot(aes(x=`WLTP-tall`, y=STOPP)) +
    geom_point(aes(y=STOPP)) +
    geom_abline(slope = 1, intercept = 0, color = "red")+
    coord_cartesian(xlim = c(300, 600), ylim = c(300, 600))+
    annotate("text", x=410, y=460, label= "WLTP range")+
    labs(title = "Range of electric cars", x = "Expected range", y = "Actual Stop (km)")+
    theme_classic()
```

```{r}
lm(STOPP ~ `WLTP-tall`, data = df_car) 


#plotting 
  df_car %>%
    ggplot(aes(x=`WLTP-tall`, y=STOPP)) +
    geom_point(aes(y=STOPP)) +
    geom_abline(slope = 1, intercept = 0, color = "red")+
    coord_cartesian(xlim = c(300, 600), ylim = c(300, 600))+
    annotate("text", x=410, y=460, label= "WLTP range")+
    labs(title = "Range of electric cars", x = "Expected range (km)", y = "Actual Stop (km)")+
    geom_smooth(method = lm)+
    theme_classic()
```

The values presented here define a linear regression function. The intercept value represents the response value (STOP) when the predictor (WLTP) is zero, while the second value indicates the expected increase in the response value for every one-unit increase in the predictor value. A one-unit increase in WLTP leads to a 0.8671 increase in STOP. The resulting linear regression function can be expressed as f(x)=-26.640+0.8671x and is displayed in the plot. This shows that the actual driving distance of the electric cars are on average 0.8671 percent of the WLTP test values.
